---
title: "MEDS Course Timeline and Descriptions"
output:
  distill::distill_article:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(googlesheets4)
library(kableExtra)
library(tidyverse)
library(here)

courses <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1uVKAYahg0z07gcafI7Gcb7ClOrJg0abuOGHrpyy_7BE/edit#gid=0") # Request access from Allison or Jamie to update this sheet

summer <- courses %>%
  filter(quarter == "Summer") %>%
  select(-quarter) %>%
  write_csv(here("course_description_files", "summer.csv"))

fall <- courses %>%
  filter(quarter == "Fall") %>%
  select(-quarter) %>%
  write_csv(here("course_description_files", "fall.csv"))

winter <- courses %>%
  filter(quarter == "Winter") %>%
  select(-quarter) %>%
  write_csv(here("course_description_files", "winter.csv"))

spring <- courses %>%
   filter(quarter == "Spring") %>%
   select(-quarter) %>%
   write_csv(here("course_description_files", "spring.csv"))

summer <- read_csv(here("course_description_files", "summer.csv"))
fall <- read_csv(here("course_description_files", "fall.csv"))
winter <- read_csv(here("course_description_files", "winter.csv"))
spring <- read_csv(here("course_description_files", "spring.csv"))
```

## Summer Intensive Courses

All MEDS students will complete 12 units of intensive coursework (early August through mid-September) to start the program. Summer courses will be held at the National Center for Ecological Analysis and Synthesis (NCEAS) in downtown Santa Barbara.

```{r, echo = FALSE}
# Update 212 title cell (w/ link)
summer[1,2] <- cell_spec("Essential Math for Environmental Data Science",  "html", link = "https://allisonhorst.github.io/EDS_212_essential-math/")

# Update 221 title cell (w/ link)
summer[2,2] <- cell_spec("Scientific Programming Essentials",  "html", link = "https://allisonhorst.github.io/EDS_221_programming-essentials/")

# Update 212 title cell (w/ link)
summer[3,2] <- cell_spec("Analytical Workflows and Scientific Reproducibility",  "html", link = "https://brunj7.github.io/EDS-214-analytical-workflows/")

# Update 215 title cell (w/ link)
summer[4,2] <- cell_spec("Introduction to Data Storage and Management",  "html", link = "https://jamesfrew.github.io/EDS_215_data_management/")

summer[5,2] <- cell_spec("Meta-analysis and Systematic Reviews",  "html", link = "https://ucsbhydro.github.io/EDS_216_meta-analysis/")

summer %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor"), format = "html", escape = FALSE) %>% 
  kable_styling(bootstrap_options = "striped") %>% 
  kableExtra::row_spec(1:5, extra_css = "border-bottom: 1px solid gainsboro") %>% 
  scroll_box(width = "100%", height = "600px")
```

</br>

## Fall Quarter

**Note:** Fall, Winter and Spring courses will utilize both of the MEDS campuses (UC Santa Barbara and NCEAS), which are ~11 miles (~20 minutes driving, ~30 minutes by bus) apart from each other. Students will only ever have planned activities at one of the campus locations on any given day. 

```{r, echo = FALSE}
# Update 213 title cell (w/ link)
fall[1,2] <- cell_spec("Metadata Standards, Data Modeling and Data Semantics",  "html", link = "https://brunj7.github.io/EDS-213-metadata/")

# Update 211 title cell (w/ link)
fall[2,2] <- cell_spec("Team Science, Collaborative Analysis and Project Management",  "html", link = "https://bbest.github.io/eds211-team/")

# Update 220 title cell (w/ link)
fall[3,2] <- cell_spec("Remote Sensing and Environmental Data",  "html", link = "https://samanthastevenson.github.io/EDS220_site/")

# Update 222 title cell (w/ link)
fall[4,2] <- cell_spec("Statistics for Environmental Data Science",  "html", link = "https://tcarleton.github.io/EDS-222-stats/")

# Update 223 title cell (w/ link)
fall[5,2] <- cell_spec("Spatial Analysis for Environmental Data Science",  "html", link = "https://jamesfrew.github.io/EDS_223_spatial_analysis/")

fall %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor"), format = "html", escape = FALSE) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(1:5, extra_css = "border-bottom: 1px solid gainsboro") %>% 
  scroll_box(width = "100%", height = "600px")
```

</br>

## Winter Quarter

```{r, echo = FALSE}
winter %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor")) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(1:4, extra_css = "border-bottom: 1px solid gainsboro") %>% 
  scroll_box(width = "100%", height = "600px")
```

</br>

## Spring Quarter

```{r, echo = FALSE}
spring %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor")) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(1:3, extra_css = "border-bottom: 1px solid gainsboro") %>% 
  scroll_box(width = "100%", height = "600px")
```
