---
title: "MEDS Course Timeline and Descriptions"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(googlesheets4)
library(kableExtra)
library(tidyverse)
library(here)

# courses <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1uVKAYahg0z07gcafI7Gcb7ClOrJg0abuOGHrpyy_7BE/edit#gid=0") # Request access from Allison or Jamie to update this sheet

# summer <- courses %>% 
#   filter(quarter == "Summer") %>% 
#   select(-quarter) %>% 
#   write_csv(here("course_description_files", "summer.csv"))
# 
# fall <- courses %>% 
#   filter(quarter == "Fall") %>% 
#   select(-quarter) %>% 
#   write_csv(here("course_description_files", "fall.csv"))
# 
# winter <- courses %>% 
#   filter(quarter == "Winter") %>% 
#   select(-quarter) %>% 
#   write_csv(here("course_description_files", "winter.csv"))
# 
# spring <- courses %>% 
#    filter(quarter == "Spring") %>% 
#    select(-quarter) %>% 
#    write_csv(here("course_description_files", "spring.csv"))

summer <- read_csv(here("course_description_files", "summer.csv"))
fall <- read_csv(here("course_description_files", "fall.csv"))
winter <- read_csv(here("course_description_files", "winter.csv"))
spring <- read_csv(here("course_description_files", "spring.csv"))
```

## Summer Intensive Courses

All MEDS students will complete 12 units of intensive coursework (early August through mid-September) to start the program. Summer courses will be held at the National Center for Ecological Analysis and Synthesis (NCEAS) in downtown Santa Barbara.

```{r, echo = FALSE}
summer %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor")) %>% 
  kable_styling(bootstrap_options = "striped") %>% 
  kableExtra::row_spec(1:5, extra_css = "border-bottom: 1px solid gainsboro")
```

## Fall Quarter

**Note:** Fall, Winter and Spring courses will utilize both of the MEDS campuses (UC Santa Barbara and NCEAS), which are ~11 miles (~20 minutes driving, ~30 minutes by bus) apart from each other. Students will only ever have planned activities at one of the campus locations on any given day. 

```{r, echo = FALSE}
fall %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor")) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(1:5, extra_css = "border-bottom: 1px solid gainsboro")
```

## Winter Quarter

```{r, echo = FALSE}
winter %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor")) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(1:4, extra_css = "border-bottom: 1px solid gainsboro")
```

## Spring Quarter

```{r, echo = FALSE}
spring %>% 
  kable(col.names = c("Course number", "Course title", "Units", "Description", "Instructor")) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(1:3, extra_css = "border-bottom: 1px solid gainsboro")
```
