---
title: "MEDS Staff & Contacts"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

##############################
# load packages
##############################

library(googlesheets4)
library(kableExtra)
library(tidyverse)

##############################
# load in google sheet - REQUEST ACCESS FROM SAM TO UPDATE THIS SHEET
##############################

contacts <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1LsjjR2DaPFgWfDqCJudNmkyNQqV9LIWbXXLm-s10PsA/edit?usp=sharing")

```

It takes a team to run any academic program smoothly, and we are grateful for ours! Get to know a bit more about our core MEDS staff and find their contact information below.

For a complete list of staff and faculty, please see the [Bren](https://bren.ucsb.edu/people/staff) and [NCEAS](https://www.nceas.ucsb.edu/about-us/our-people) websites.

## MEDS Staff & Faculty

#### `r fontawesome::fa("code", fill = "#047C90", a11y = "sem")` Programmatic & Training

* [Jamie Montgomery](https://www.jamiecmontgomery.com/) (*she/her*) | **MEDS Program Coordinator** | NCEAS 103 & Bren Hall 4402  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` jmontgomery@bren.ucsb.edu  
<span style = 'font-size:95%;'>*As coordinator, Jamie oversees all aspects of the program and works closely with other Bren staff to guide admissions, recruitment, student affairs, academic programs and career development.*</span>

* [Allison Horst](https://www.allisonhorst.com/) (*she/her*) | **Assistant Teaching Professor** | Bren Hall 4406  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` ahorst@bren.ucsb.edu  
<span style = 'font-size:95%;'>*Allison teaches Essential Math for Environmental Data Science, Scientific Programming Essentials, and the MEDS Capstone course to facilitate student progress on their 6-month group capstone project as a faculty advisor. She actively works to contribute open educational resources, including software for data science education, and artwork for data science & stats teachers and learners.*</span>

* [Sam Csik](https://samanthacsik.github.io/) (*she/her*) | **Data Training Coordinator** | NCEAS 103  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` scsik@ucsb.edu  
<span style = 'font-size:95%;'>*Sam develops and teaches data science workshops for MEDS students, which are meant to supplement the MEDS curriculum. She was once named one of the three “kooky data science aunts” (along with Jamie Montgomery and Allison Horst) by an anonymous MEDS student and she wears that title proudly. You will be seeing lots of her around NCEAS helping out where needed throughout the program. If you ever have any questions about data science, ecology, grad school, life in SB, etc. or have an idea for a workshop, stop by her office or send her an email at any time!*</span>

#### `r fontawesome::fa("laptop", fill = "#047C90", a11y = "sem")` Compute  
* [Kat Le](https://bren.ucsb.edu/people/kat-le) (*she/her*) | **Science Programming & Technical Support Analyst** | Bren Hall 3516  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` kat@bren.ucsb.edu  
<span style = 'font-size:95%;'>*coming soon*</span>

#### `r fontawesome::fa("pencil-alt", fill = "#047C90", a11y = "sem")` Capstone  
* [Emily Case](https://bren.ucsb.edu/people/emily-case) (*she/her*) | **Academic Programs & Capstone Coordinator**| Bren Hall 2439  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` ecase@bren.ucsb.edu   
<span style = 'font-size:95%;'>*As the Academic Programs and Capstone Coordinator for the Bren School, Emily is responsible for supporting academic programs, curriculum planning, Capstone and Master’s Group Projects, academic requirements, and various programmatic initiatives. She works closely with the Assistant Dean, as well as faculty and staff, in order to ensure educational effectiveness and program competitiveness.*</span>

#### `r fontawesome::fa("handshake", fill = "#047C90", a11y = "sem")` Career
* [Miya Scheble](https://bren.ucsb.edu/people/miya-scheble) (*she/her*) | **MEDS Career Development Program Manager** | Bren Hall 2522  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` miya@bren.ucsb.edu  
<span style = 'font-size:95%;'>*Miya manages the Master of Environmental Data Science (MEDS) Career Development Program. She oversees day-to-day operations and provides career development advising services within a variety of areas, including career direction support, job search strategy, networking opportunities, and document review for both MEDS and MESM students.*</span>

#### `r fontawesome::fa("graduation-cap", fill = "#047C90", a11y = "sem")` Admissions & Student Affairs
* [Kimberly Yom](https://bren.ucsb.edu/people/kimberly-yom) (*she/her*) | **MEDS Admissions and Student Affairs Coordinator**  
`r fontawesome::fa("envelope", fill = "#047C90", a11y = "sem")` kyom@bren.ucsb.edu  
<span style = 'font-size:95%;'>*As the Master of Environmental Data Science (MEDS) Admissions and Student Affairs Coordinator, Kimberly provides ancillary services for the MEDS program, handling outreach efforts for prospective students, managing applications and analyzing their data, and advising students on matters involving admissions, program logistics, course enrollment, and degree requirements.*</span>


```{r, echo = FALSE}
##############################
# subset
##############################

# programmatic_training <- contacts %>% 
#   filter(Department == "training_programmatic") %>% 
#   select(-Department)

##############################
# add links
##############################

# programmatic & training
# contacts[1,2] <- cell_spec("Jamie Montgomery (she/her)",  "html", link = "https://www.jamiecmontgomery.com/")
# contacts[2,2] <- cell_spec("Allison Horst (she/her)",  "html", link = "https://www.allisonhorst.com/")
# contacts[3,2] <- cell_spec("Sam Csik (she/her)",  "html", link = "https://samanthacsik.github.io/")

##############################
# build table 
##############################

# contacts %>% 
#   kable(col.names = c("Department", "Name (pronouns)", "Position", "Bio", "Office & Email"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
  # kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
  #scroll_box(width = "100%", height = "400px") 
```

## Email Request Queues

Have a question about MEDS/Bren? The Bren School has established request queues for help, repairs, and frequently needed services. Please use the appropriate email queue so that your question/request can be properly directed and handled. The most commonly used request queues are listed below. For a full list, please visit Bren's [Administrative Services page](https://bren.ucsb.edu/administrative-services-current-students).

* **academics@bren.ucsb.edu**: For current students to obtain information and/or request assistance in regards to registering for classes, grade reporting, book orders, approval codes, and other instructional support issues.*This is the most commonly used queue for current students and a great place to start if you don't know where to direct your request.*

* **admissions@bren.ucsb.edu**: To obtain information about our academic programs, applying to one of our programs, open houses, and visiting the Bren School.
 
* **brenhall@bren.ucsb.edu**: To submit trouble tickets for operational and building-related issues.

* **medscareer@bren.ucsb.edu**: For current students to obtain information and/or request assistance from the career development staff, to submit a job opening for alumni.

* **compute@bren.ucsb.edu**: To report issues relating to networks or computers or other hardware/software problems at the Bren school.

* **finance@bren.ucsb.edu**: For inquiries related to accounts, budgets, late payments, general finance issues, etc.

* **scheduling@bren.ucsb.edu**: For assistance booking/scheduling rooms and meeting spaces beyond what can be booked through booking.bren.ucsb.edu for Bren students, staff, and faculty. 
