---
title: "Past MEDS Workshops"
author: "sam"
date: "2022-08-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Past Workshops

Workshops from past years, which are likely to be updated soon!

---

`r fontawesome::fa("css3-alt", fill = "#003660", a11y = "sem")` **Customizing Your Personal Website with CSS (and some other stuff)** | August 31, 2021 | ~1 hour

<span style = 'font-size:95%;'>[`r fontawesome::fa("tv", fill = "#64605F", a11y = "sem")` slides](https://ucsb-meds.github.io/customizing-websites-css/#1)  |  [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/customizing-websites-css)</span> 

<span style = 'font-size:95%; color:#959599;'>*A brief introduction to using CSS to customize {distill} websites. Topics include (a) an intro to HTML & CSS, (b) changing default element styling (fonts, colors, sizes), (c) creating custom CSS rules, (d) finding inspiration from other distill websites & adapting their open source code, (d) adding a CV to your personal site.*</span>

---

`r fontawesome::fa("blog", fill = "#003660", a11y = "sem")` **Writing data science-related blog posts for your personal website** | September 29, 2021 | ~1 hour

<span style = 'font-size:95%;'>[`r fontawesome::fa("blog", fill = "#64605F", a11y = "sem")` blog post](https://samanthacsik.github.io/posts/2021-09-21-my-first-test-post/)  |  [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/writing-blogposts)</span> 

<span style = 'font-size:95%; color:#959599;'>*Take your blog posts further with some additional training on post customization! You may be asked to create blog posts as part of your course assignments, so this workshop is designed to give you some more tools in writing good blog posts.*</span>

---

`r fontawesome::fa("google", fill = "#003660", a11y = "sem")` **Teach Me How to Google** | October 11, 2021 | ~1 hour

<span style = 'font-size:95%;'>[`r fontawesome::fa("tv", fill = "#64605F", a11y = "sem")` slides](https://ucsb-meds.github.io/teach-me-how-to-google/#1)  |  [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/teach-me-how-to-google)</span> 

<span style = 'font-size:95%; color:#959599;'>*Googling for code help is something that all data scientists (at all career stages) do. But figuring out how to get the information you need back can be incredibly challenging, particularly for new coders. In this workshop, we’ll discuss strategies for refining your queries to increase your chances of finding informative solutions.*</span>

---

`r fontawesome::fa("google", fill = "#003660", a11y = "sem")` **RStudio Tips & Tricks (and other keyboard shortcuts to make you a more efficient coder)** | November 15, 2021 | ~1 hour

<span style = 'font-size:95%;'>[`r fontawesome::fa("tv", fill = "#64605F", a11y = "sem")` slides](https://ucsb-meds.github.io/R-tips-and-tricks/#1)  |  [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/R-tips-and-tricks)</span> 

<span style = 'font-size:95%; color:#959599;'>*As environmental data scientists, we spend a lot of time in RStudio. Taking some time to learn how you can customize your RStudio IDE (Integrated Development Environment) and the keyboard shortcuts used to navigate around that IDE can make you a more efficient (and happier) hacker!*</span>

---

`r fontawesome::fa("google", fill = "#003660", a11y = "sem")` **Programming with Python & Intro to Webscraping** | January 4, 2022 | ~8 hour

<span style = 'font-size:95%;'>[`r fontawesome::fa("file-alt", fill = "#64605F", a11y = "sem")` instructional documentation](https://ucsbcarpentry.github.io/2022-01-04-ucsb-python/)  |  [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSBCarpentry/2022-01-04-ucsb-python)</span> 

<span style = 'font-size:95%; color:#959599;'>*This workshop, presented by Data Carpentries instructors, Greg Janée and Amanda Ho, provides an introduction to programming with Python and covers data wrangling with Pandas, writing loops and functions, data visualization with plotnine, and webscraping with Pandas.*</span>



```{r icon-links, eval=TRUE, echo=FALSE}
# distilltools::icon_link(
#     icon = "fas fa-tv",
#     text = "slides",
#     url = "https://ucsb-meds.github.io/cloud-computing/#1")
# 
# 
# distilltools::icon_link(
#   icon = "fas fa-github",
#   text = "source code",
#   url = "https://github.com/UCSB-MEDS/cloud-computing")
```




```{r, echo = FALSE}
# Summer

# ##############################
# # add links
# ##############################
# 
# # CSS
# summer_workshops[1,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/customizing-websites-css/#1")
# summer_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/customizing-websites-css")
# 
# ##############################
# # build table 
# ##############################
# 
# summer_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```

```{r, echo = FALSE}
## Fall Workshops 

# ##############################
# # add links
# ##############################\
# 
# # Blog
# fall_workshops[1,5] <- cell_spec("link",  "html", link = "https://samanthacsik.github.io/posts/2021-09-21-my-first-test-post/")
# fall_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/writing-blogposts")
# 
# # Google
# fall_workshops[2,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/teach-me-how-to-google/#1")
# fall_workshops[2,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/teach-me-how-to-google")
# 
# # RStudio Tips & Tricks
# fall_workshops[3,5] <- cell_spec("link", "html", link = "https://ucsb-meds.github.io/R-tips-and-tricks/#1")
# fall_workshops[3,6] <- cell_spec("link", "html", link = "https://github.com/UCSB-MEDS/R-tips-and-tricks")
# 
# ##############################
# # build table 
# ##############################
# 
# fall_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```

```{r, echo = FALSE}
## Winter Workshops

# ##############################
# # add links
# ##############################
# 
# # Python (by Data Carpentries)
# winter_workshops[1,5] <- cell_spec("link",  "html", link = "https://ucsbcarpentry.github.io/2022-01-04-ucsb-python/")
# winter_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSBCarpentry/2022-01-04-ucsb-python")
# 
# # SQL (by Data Carpentries)
# winter_workshops[2,5] <- cell_spec("link",  "html", link = "https://ucsbcarpentry.github.io/2022-02-04-ucsb-sql-online/")
# winter_workshops[2,6] <- cell_spec("link",  "html", link = "https://github.com/UCSBCarpentry/2022-02-04-ucsb-sql-online")
# 
# # Intro to Shiny
# winter_workshops[3,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/shiny-workshop/#1")
# winter_workshops[3,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/shiny-workshop")
# 
# ##############################
# # build table 
# ##############################
# 
# winter_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```

```{r, echo = FALSE}
## Spring Workshops

# ##############################
# # add links
# ##############################
# 
# # Intro to Cloud Computing
# spring_workshops[1,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/cloud-computing/#1")
# spring_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/cloud-computing")
# 
# # Technical Interviews
# spring_workshops[2,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/technical-interviews/#1")
# spring_workshops[2,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/technical-interviews")
# 
# ##############################
# # build table 
# ##############################
# 
# spring_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```
