---
title: "Workshop Materials"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We are actively developing data science workshops, which are meant to supplement the MEDS curriculum and teach additional skills. Below are our most up-to-date materials, presented to our current cohort of students. Find older workshop materials on our [Past Workshop Materials page](past_workshops.html).

---

:::: {style="display: grid; grid-template-columns: 0.5fr 2fr; grid-column-gap: 10px;"}

::: {}

August 5, 2022 

:::


::: {}

`r fontawesome::fa("window-maximize", fill = "#333333", a11y = "sem")` **Creating your personal website using Quarto**  

<span style = 'font-size:95%;'>[`r fontawesome::fa("file-alt", fill = "#64605F", a11y = "sem")` instructional documentation](https://ucsb-meds.github.io/creating-quarto-websites/) | [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/creating-quarto-websites)</span> 

<span style = 'font-size:95%; color:#959599;'>*A personal website is not only a great way to showcase your experiences and skills, but also gives people (potential employers included!) a better sense of who you are as a person. There are lots of great ways to build websites using R (e.g. `{distill}`, `{blogdown}`) -- this year, we'll be using [Quarto](https://quarto.org/), an exciting, new, and versatile publishing tool that supports R, Python, Julia, and ObservableJS.*</span>

:::

::::

---

:::: {style="display: grid; grid-template-columns: 0.5fr 2fr; grid-column-gap: 10px;"}

::: {}

August 18, 2022

:::


::: {}

<span style = 'font-size:110%;'>`r fontawesome::fa("google", fill = "#333333", a11y = "sem")` **Teach Me How to Google**</span>

<span style = 'font-size:95%;'>[`r fontawesome::fa("tv", fill = "#64605F", a11y = "sem")` slides](https://ucsb-meds.github.io/teach-me-how-to-google/#1)  |  [`r fontawesome::fa("github-square", fill = "#64605F", a11y = "sem")` source code](https://github.com/UCSB-MEDS/teach-me-how-to-google)</span> 

<span style = 'font-size:95%; color:#959599;'>*Googling for code help is something that all data scientists (at all career stages) do. But figuring out how to get the information you need back can be incredibly challenging, particularly for new coders. In this workshop, we’ll discuss strategies for refining your queries to increase your chances of finding informative solutions. [Approx. Duration: 1.5 hours]*</span>

:::

::::

---

<h2 align="center">[Find past workshop materials here!](past_workshops.html)</h2>







```{r, echo = FALSE}
# OLD

# ##############################
# # load packages
# ##############################
# 
# library(googledrive)
# library(googlesheets4)
# library(kableExtra)
# library(tidyverse)
# library(here)
# 
# ##############################
# # load in google sheet - REQUEST ACCESS FROM SAM TO UPDATE THIS SHEET
# ##############################
# 
# workshops <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1SQ2IL8VP4McfCzvEeHjl0K6844j5l_5BfUTcS9_y4C4/edit?usp=sharing")
# 
# ##############################
# # filter for quarter
# ##############################
# 
# summer_workshops <- workshops %>% 
#   filter(Quarter == "summer") %>% 
#   select(-Quarter)
# 
# fall_workshops <- workshops %>% 
#   filter(Quarter == "fall") %>% 
#   select(-Quarter)
# 
# winter_workshops <- workshops %>% 
#   filter(Quarter == "winter") %>% 
#   select(-Quarter)
# 
# spring_workshops <- workshops %>% 
#   filter(Quarter == "spring") %>% 
#   select(-Quarter)
```

```{r, echo = FALSE}
# Summer

# ##############################
# # add links
# ##############################
# 
# # CSS
# summer_workshops[1,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/customizing-websites-css/#1")
# summer_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/customizing-websites-css")
# 
# ##############################
# # build table 
# ##############################
# 
# summer_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```

```{r, echo = FALSE}
## Fall Workshops 

# ##############################
# # add links
# ##############################\
# 
# # Blog
# fall_workshops[1,5] <- cell_spec("link",  "html", link = "https://samanthacsik.github.io/posts/2021-09-21-my-first-test-post/")
# fall_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/writing-blogposts")
# 
# # Google
# fall_workshops[2,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/teach-me-how-to-google/#1")
# fall_workshops[2,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/teach-me-how-to-google")
# 
# # RStudio Tips & Tricks
# fall_workshops[3,5] <- cell_spec("link", "html", link = "https://ucsb-meds.github.io/R-tips-and-tricks/#1")
# fall_workshops[3,6] <- cell_spec("link", "html", link = "https://github.com/UCSB-MEDS/R-tips-and-tricks")
# 
# ##############################
# # build table 
# ##############################
# 
# fall_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```

```{r, echo = FALSE}
## Winter Workshops

# ##############################
# # add links
# ##############################
# 
# # Python (by Data Carpentries)
# winter_workshops[1,5] <- cell_spec("link",  "html", link = "https://ucsbcarpentry.github.io/2022-01-04-ucsb-python/")
# winter_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSBCarpentry/2022-01-04-ucsb-python")
# 
# # SQL (by Data Carpentries)
# winter_workshops[2,5] <- cell_spec("link",  "html", link = "https://ucsbcarpentry.github.io/2022-02-04-ucsb-sql-online/")
# winter_workshops[2,6] <- cell_spec("link",  "html", link = "https://github.com/UCSBCarpentry/2022-02-04-ucsb-sql-online")
# 
# # Intro to Shiny
# winter_workshops[3,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/shiny-workshop/#1")
# winter_workshops[3,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/shiny-workshop")
# 
# ##############################
# # build table 
# ##############################
# 
# winter_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```

```{r, echo = FALSE}
## Spring Workshops

# ##############################
# # add links
# ##############################
# 
# # Intro to Cloud Computing
# spring_workshops[1,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/cloud-computing/#1")
# spring_workshops[1,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/cloud-computing")
# 
# # Technical Interviews
# spring_workshops[2,5] <- cell_spec("link",  "html", link = "https://ucsb-meds.github.io/technical-interviews/#1")
# spring_workshops[2,6] <- cell_spec("link",  "html", link = "https://github.com/UCSB-MEDS/technical-interviews")
# 
# ##############################
# # build table 
# ##############################
# 
# spring_workshops %>% 
#   kable(col.names = c("Date", "Workshop title", "Description", "Approximate duration", "Presentation materials", "GitHub repo"), format = "html", escape = FALSE) %>% 
#   kable_styling(bootstrap_options = "striped") %>% 
#   kableExtra::row_spec(1, extra_css = "border-bottom: 1px solid gainsboro") # %>% 
#   #scroll_box(width = "100%", height = "400px") 
```
